### 2020-09-26 paper/sections/introduction.tex
add some figures

Apparently, choosing different configurations will affect resource consumption and accuracy. For example, using a complex model with high resolution can obviously and accurately detect the target object, but it also requires more computing resources. However, choosing a simple model with low resolution can significantly reduce resource consumption, although it reduces the accuracy to some extent. Obviously, when the target car (object) is large, a smaller model and a lower resolution can meet the accuracy with a large reduction of resource consumption, while the target car (object) is small, a more complex model and higher resolution are needed to achieve a satisfactory accuracy. And in the case of a highway video analytics, due to the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) instead of having to use a constant high frame rate throughout whole video. This can significantly reduce resource consumption, but does not affect the accuracy of the video analytics.

>>>>

Apparently, choosing different configurations will affect resource consumption and accuracy. As shown in~\autoref{fig1}, at a fixed frame rate, using a complex model with high resolution(such as FasterRCNN+InceptionResnet 1024p) can obviously and accurately detect the target object, but it also requires more computing resources. However, when using the same model, choosing a lower resolution can reduce the computing resources, and the subsequent cost is the decline of accuracy. Another example is that choosing a simple model with low resolution(such as FasterRCNN+ResNet50 640p) can significantly reduce resource consumption, although it reduces the accuracy to some extent. Obviously, when the target car (object) is large, a smaller model and a lower resolution can meet the accuracy with a large reduction of resource consumption, while the target car (object) is small, a more complex model and higher resolution are needed to achieve a satisfactory accuracy. And in the case of a highway video analytics, due to the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) instead of having to use a constant high frame rate throughout whole video. This can significantly reduce resource consumption, but does not affect the accuracy of the video analytics. We use~\autoref{fig2} to support that, the data in this figure come from a real road. It can be found that with the decrease of frame rate, the resource consumption can be significantly reduced, but the decrease of accuracy is partly acceptable.

\begin{figure}[h]
\includegraphics[width=9cm,height=5cm]{figures/figure1.jpg}
\centering
\caption{The effect of different models and resolutions on accuracy and processing time at a fixed frame rate.}
\label{fig1}
\end{figure}

\begin{figure}[h]
\includegraphics[width=9cm,height=5cm]{figures/figure2.jpg}
\centering
\caption{Under the best model, the accuracy and processing time vary with the different frame rate.}
\label{fig2}
\end{figure}
